Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-10 paper/disc20clustering.tex
Comments
wip
Distributed

\begin{theorem}
	\TAlg is $(60\ell)$-competitive for $k=3$.
\end{theorem}
\begin{proof}
	Fix a completed phase, and consider the state of \TAlg's counters at the end of it (before the reset).
	We consider the incomplete phase later in this proof.

@@

\noindent
\textbf{Approximation for offline rematching.}
\maciek{Maybe mention the offline approx here?}

@@

\mahmoud{mention the offline approx.}
While we have described our algorithms globally so far, we note that these allow for efficient distributed implementations. 
The algorithm PPL from Section~\ref{sec:ppl} can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The algorithm for $k=2$ from Section~\ref{sec:k2} performs only local communication for each request: counters are kept on the clusters and updated locally, and each migration concerns only two clusters.
\medskip
Now, we propose the distributed implementation of the algorithm for $k=3$ from Section~\ref{sec:k3}.
The algorithm performs two non-local operations:
\begin{enumerate}
	\item Broadcasting the end of the phase.\label{it:broadcast}
	\item Component merge.
	\label{it:merge}
\end{enumerate}

If a component reaches size $4$ or a fresh cluster is not found, we conclude that no perfect partition exists.
Then, we end the phase and broadcast the message to  reset the counters in all clusters.

A merge of two components may require finding a third cluster that contains $3$ isolated nodes (for details see the proof of Lemma~\ref{lem:1req})).
We say that a cluster containing $3$ isolated nodes is \emph{fresh}.
In the following, we show how to efficiently find a fresh cluster in a distributed manner.
We organize the clusters into an arbitrary rooted balanced binary tree, and we broadcast the root to each cluster.
Each cluster maintains the counter of fresh clusters in its subtree.
To find a fresh cluster, we traverse an arbitrary path of non-zero counters from the root.
Upon encountering a fresh cluster, we stop the traversal and decrease the counters on the followed path by $1$.

The operation (\ref{it:broadcast}) requires a single broadcast, and the operation (\ref{it:merge}) requires $O(\log \ell)$ communication.
Each of these may occur, on average, every $\alpha$ external requests.

@@

@@

>>>>

\begin{theorem}
	\TAlg is $60\ell$-competitive for $k=3$.
\end{theorem}
\begin{proof}
	Fix a completed phase, and consider the state of \TAlg's counters at the end of it (before the reset).
	We consider the incomplete phase later in this proof.

@@

\noindent
\textbf{Approximation for offline rematching.}
\maciek{Maybe mention the offline approx here instead of the next section? similar to e.g. the remarks after the LB}

\mahmoud{mention the offline approx.}

@@

@@

\medskip
\noindent
\textbf{Distributed implementation.}
While we have described our algorithms globally so far, we note that these allow for efficient distributed implementations. 
The algorithm PPL from Section~\ref{sec:ppl} can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The algorithm for $k=2$ from Section~\ref{sec:k2} performs only local communication for each request: counters are kept on the clusters and updated locally, and each migration concerns only two clusters.

Furthermore, we propose an efficient distributed implementation of the algorithm for $k=3$ from Section~\ref{sec:k3}.
The algorithm performs two types of operations that require communication with other clusters: a~component merge, and a broadcast of the end of the phase.
We say that a cluster containing $3$ isolated nodes is \emph{fresh}.
A merge of two components may require finding a fresh cluster (for details see the proof of Lemma~\ref{lem:1req})).
In the following, we show how to efficiently find a fresh cluster in a distributed manner.
We organize the clusters into an arbitrary rooted balanced binary tree, and we broadcast the root to each cluster.
Each cluster maintains the counter of fresh clusters in its subtree.
To find a fresh cluster, we traverse an arbitrary path of non-zero counters from the root.
Upon encountering a fresh cluster, we end the traversal and decrease the counters on the followed path by $1$.
Summarizing, ending the phase requires a single broadcast, and merging components requires $O(\log \ell)$ communication.

@@

\maciek{Make it more general (essentially the pseudocode of DET) to also link to this section from k=3.}

\maciek{todo: intro to the algorithm (mostly about the choice of repartition procedure in \TAlg and PPL)}
